A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-22 colt-21/cvx-flats.tex
Fixing typos and adding questions

	(1.)
	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
	In particular, for $q \in F$, we have $q_\alpha \in F$.
	Therefore, $p \in \relint{F}$.

@@

	(2.)
	Let $p \in \relint{\P} \cap F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for that function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
	(Such a function must exist by $F$ being a $d$-representation.)

@@

	Suppose $v \in F_p$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
	The result follows by applying the definition of Feasible Subspaces.	
\end{proof}

>>>>

	(1.)
	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
	In particular, for $q \in F$, we have $q_\alpha \in F$.
	Therefore, $p \in \relint{F}$. \jessie{Feels insufficient}

@@

	(2.)
	Let $p \in F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
	(Such a function must exist by $F$ being a $d$-representation.)

@@

	Suppose $v \in F_p$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex. %, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
	The result follows by applying the definition of the subspace of feasible directions.	
\end{proof}
